Stellar Radiation is Critical for Regulating Star Formation and Driving Outflows in Low Mass Dwarf Galaxies

### 2018-08-01 ms.tex
Update on Overleaf.

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{galaxies -- feedback -- galaxy evolution -- galactic winds}

@@

\section{Discussion} \label{sec:discussion}
Accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows. We believe this work is novel in examining the
importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star. Modeling only local stellar ionizing feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy. To explore the cause of this difference we compare in Figure~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See ({\it insert link here once posted}) for a movie of this comparison.}

>>>>

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{galaxies -- feedback -- galaxy evolution}

@@

\section{Discussion} \label{sec:discussion}
Accounting for feedback from stellar radiation plays a significant role in determining the ability for SN energy to couple to the ISM and therefore drive outflows. We believe this work is novel in examining the
importance of localized ionization vs.\ ionization from a diffuse radiation field far from a single star. Modeling only local stellar ionizing feedback is insufficient to describe the long-term evolution of an isolated dwarf galaxy. To explore the cause of this difference we compare in Figure~\ref{fig:panel1} and~Figure~\ref{fig:panel2} the gas number density (left), temperature (middle), and hydrogen ionization fraction (right) in edge-on slices in each of our simulations at two different times.\footnote{See https://youtu.be/r1nEW6Yu3xI for a movie of this comparison.}
